Evolution of pre-copulatory and post-copulatory inbreeding behaviour

### 2016-10-27 ms_pre_post.Rmd
Add new call to DOCX template, nicer?

---
title: "Evolution of pre-copulatory and post-copulatory inbreeding behaviour"
author: "A. Bradley Duthie et al."
date: "August 24, 2016"
output:
  pdf_document:
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution.csl
header-includes:
- \usepackage{natbib}
- \usepackage{lineno}
- \linenumbers
- \bibliographystyle{amnatnat}
linestretch: 2
csl: evolution.csl
bibliography: ms_pre_post.bib
---

>>>>

---
title: "Evolution of pre-copulatory and post-copulatory inbreeding behaviour"
author: "A. Bradley Duthie et al."
date: "August 24, 2016"
output:
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution.csl
    reference_docx: docx_template.docx
  pdf_document:
    fig_caption: yes
  html_document: default
header-includes:
- \usepackage{natbib}
- \usepackage{lineno}
- \linenumbers
- \bibliographystyle{amnatnat}
linestretch: 2
csl: evolution.csl
bibliography: ms_pre_post.bib
---
